method

### 2022-02-08 06_Paper/ER-ED/method.Rmd
BF ANOVA Ratings View

library(targets)    # to keep track of all relevant files
library(readxl)     # import excel files
library(here)       # to set directories without defined paths
library(papaja)     # APA conform output
library(afex)       # for ANOVA
library(emmeans)
library(ggplot2)    # for nice plots
library(dplyr)

@@

arousal_view = data_ER %>%
  subset(data_ER$block == "view_neu" | data_ER$block == "view_neg")

aov_arousalView = afex::aov_ez(data = arousal_view,
                               id = "ID",
                               dv = "arousal",
                               within = "block",
                               fun_aggregate = mean,
                               include_aov = TRUE)

# compute posthoc tests for within measures
posthoc_arousalView = emmeans::emmeans(aov_arousalView$aov, specs = "block")
#pairs(posthoc_arousalView, adjust = "bonferroni")

>>>>

library(targets)    # to keep track of all relevant files
library(readxl)     # import excel files
library(here)       # to set directories without defined paths
library(papaja)     # APA conform output
library(afex)       # for ANOVA
library(emmeans)
library(ggplot2)    # for nice plots
library(dplyr)
library(BayesFactor)

@@

Ratings_view <- data_ER %>%
  subset(data_ER$block == "view_neu" | data_ER$block == "view_neg")
Ratings_view$block <- as.factor(Ratings_view$block)

SubjArousalView_aov <- afex::aov_ez(data = Ratings_view,
                               id = "ID",
                               dv = "arousal",
                               within = "block",
                               fun_aggregate = mean,
                               include_aov = TRUE)

# compute posthoc tests for within measures
SubjArousalView_emm <- emmeans::emmeans(SubjArousalView_aov$aov, specs = "block")
#pairs(posthoc_arousalView, adjust = "bonferroni")

SubjArousalView_con <- as.data.frame(pairs(SubjArousalView_emm, adjust = "bonferroni"))

# Bayes Factors
SubjArousalView_BF <- BayesFactor::anovaBF(formula = arousal ~ block,
                                           data = Ratings_view,
                                           progress = FALSE)
SubjArousalView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_view$arousal[Ratings_view$block == "view_neu"],
                                                                        y = Ratings_view$arousal[Ratings_view$block == "view_neg"]))
